Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
remove hyphen

We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
both based on the Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
We provide two alternative automated procedures to synthesize safe 
digital state-feedback controls
and prove their soundness by encompassing errors due to digitalization and quantization 
effects that are present in the digital controller interacting with the continuous plant. 
Both models synthesize sound safe controllers given a discrete-time model of the closed-loop system.

>>>>

We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
both based on the CounterExample Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
We provide two alternative automated procedures to synthesize safe 
digital state-feedback controls
and prove their soundness by encompassing errors due to digitalization and quantization 
effects that are present in the digital controller interacting with the continuous plant. 
Both models synthesize sound safe controllers given a discrete-time model of the closed-loop system.
